---
title: "Assignment1"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Weather dataset downloaded from: https://vincentarelbundock.github.io/Rdatasets/articles/data.html

Documentation: https://vincentarelbundock.github.io/Rdatasets/doc/mosaicData/Weather.html

Importing the dataset into R:

```{r}
weather <- read.csv("C:/Users/lmszr/Documents/School/Fundamentals of Machine Learning/Weather.csv")
```

Descriptive summary

```{r}
summary(weather)
```

Mean of average temperatures:

```{r}
mean(weather$avg_temp)
```


Standard deviation of average temperatures:

```{r}
sd(weather$avg_temp)
```

IQR of average temperatures:

```{r}
IQR(weather$avg_temp)
```


Count of different weather events:

```{r}
table(weather$events)
```


Log transform average temperature and print short sample:
```{r}
avg_temp_log <- log(weather$avg_temp)
avg_temp_log[1:10]
```
Average temperature histogram:
```{r}
hist(weather$avg_temp, xlab = 'Average Temp', ylab = 'Days', main = 'Average Temperature')

```

Scatterplot of average temperature and average humidity:

```{r}
plot(weather$avg_temp, weather$avg_humidity, xlab = 'Average Temp', ylab = 'Average Humidity')
```
