---
output:
  pdf_document: default
  html_document: default
---
Load dataset / libraries

```{r}
library(tidyverse)
library(factoextra)
library(ISLR)
library(flexclust)
Pharma <- read.csv('C:/Users/lmszr/Documents/School/Fundamentals of Machine Learning/Pharmaceuticals.csv')
set.seed(123)
```

a. Use only the numerical variables (1 to 9) to cluster the 21 firms. Justify the various choices made in 
conducting the cluster analysis, such as weights for different variables, the specific clustering algorithm(s) 
used, the number of clusters formed, and so on. 

```{r}
Pharma_s <- Pharma[, c(3:11)]
summary(Pharma_s)
```

Scaling the data frame

```{r}
Pharma_s <-scale(Pharma_s)
distance <- get_dist(Pharma_s)
fviz_dist(distance)
```
Determine best K

```{r}
fviz_nbclust(Pharma_s, kmeans, method = "wss")
fviz_nbclust(Pharma_s, kmeans, method = "silhouette")
```
Silouhette says K =5 is optimal, but looking at WSS k=4 could be better, so I tried both.

Cluster the data

```{r}
k5 <-kmeans(Pharma_s, centers = 5, nstart = 30)
k5$centers
k5$size
fviz_cluster(k5, data = Pharma_s)
```
I don't think the suggested 5 clusters is that useful as cluster 5 only consists of 2 data points. The analyst is looking for an overview of the pharmaceutical market and it is not as meaningful in that sense, so I tried this with K = 4:

```{r}
k4 <-kmeans(Pharma_s, centers = 4, nstart = 30)
k4$centers
k4$size
fviz_cluster(k4, data = Pharma_s)
```

b. Interpret the clusters with respect to the numerical variables used in forming the clusters. 

Group 1: 2, 6, 18

Market_Cap: Lower than average
Beta: Higher than average
PE_Ratio: Higher than average (highest of all groups)
ROE: Lower than average (lowest of all groups)
ROA: Lower than average (lowest of all groups)
Asset_turnover: Around average
Leverage: Lower than average
Rev_Growth: Lower than average
Net_Profit_Margin: Lower than average (lowest of all groups)

Group 2: 1, 3, 4, 7, 10, 16, 19, 21

Market_Cap: Slightly lower than average
Beta: Lower than average (lowest of all groups)
PE_Ratio: Lower than average
ROE: Higher than average
ROA: Higher than average 
Asset_turnover: Slightly higher than average
Leverage: Lower than average
Rev_Growth: Lower than average (lowest of all groups)
Net_Profit_Margin: Higher than average

Group 3: 17, 13, 15, 11

Market_Cap: Higher than average (highest of all groups)
Beta: Lower than average 
PE_Ratio: Lower than average
ROE: Higher than average (highest of all groups)
ROA: Higher than average (highest of all groups)
Asset_turnover: Higher than average (highest of all groups)
Leverage: Lower than average
Rev_Growth: Higher than average
Net_Profit_Margin: Higher than average

Group 4: 5, 8, 9, 12, 14, 20

Market_Cap: Lower than average (lowest of all groups)
Beta: Higher than average (highest of all groups)
PE_Ratio: Lower than average (lowest of all groups)
ROE: Lower than average
ROA: Lower than average
Asset_turnover: Lower than average (lowest of all groups)
Leverage: Higher than average (highest of all groups)
Rev_Growth: Higher than average (highest of all groups)
Net_Profit_Margin: Lower than average

c. Is there a pattern in the clusters with respect to the numerical variables (10 to 12)? (those not used in forming the clusters) 

```{r}
table(Pharma[c(2, 6, 18), c(12:14)])
```

Group 1: They are all on NYSE, 2/3 are Hold, All in different countries

```{r}
table(Pharma[c(1, 3, 4, 7, 10, 16, 19, 21), c(12:14)])
```

Group 2: All on NYSE, 4/8 are Hold, 2/8 are Moderate Sell, then 1/8 each Moderate Buy and Strong Buy, 5/8 in the US, 2/8 in UK, and 1 in Switzerland.

```{r}
table(Pharma[c(17, 13, 15, 11), c(12:14)])
```

Group 3: 

```{r}
table(Pharma[c(5, 8, 9, 12, 14, 20), c(12:14)])
```

Group 4: All on different Exchanges, 4/6 are in the US, 3/6 are Moderate Buy, 2/6 are Moderate Sell, and 1/6 is Hold.

D. Provide an appropriate name for each cluster using any or all of the variables in the dataset.

Group 1: Medium-Low Market Cap and Low Rev Growth
Group 2: Medium Market Cap and Lowest Rev Growth
Group 3: Highest Market Cap and High Rev Growth
Group 4: Lowest Market Cap and Highest Rev Growth
